\texttt EPQ Key Exchange

### 2017-04-30 latex/keyexchange/secretkeybasedpublickeyencryption.tex
updated implementation for a design

Where $log(e_0) \equiv log(gcd(p_1, p_2))$.

@@

\subsubsection{Additional Information for Key Generation}
$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$. To instantiate the key exchange scheme, $log(s_1) \equiv $

@@

Secondly, this feature allows for the disassociation of the owner of the public key from the possessor of the public key. For example, assume we have three parties, Alice, Bob, and Charlie. Charlie does not want Alice to communicate with Bob. If Charlie searches Alices computer and he finds Bobs public key, then he will know that Alice has been or intended to communicate with Bob. To counter this, Alice can randomize Bobs public key and store only the randomized key. The randomized key will be functionally equivalent to the public key associated with Bob, with the exception that nobody may associate it with Bob.

>>>>

Where $log(e_0) \equiv log(gcd(p_1, p_2))$. If $p_1$ and $p_2$ are not coprime, then a simple modulo operation will yield $log(gcd(p_1, p_2))$ bits of the secret $e$.

@@

\subsubsection{Additional Information for Key Generation}
$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$. To instantiate the key exchange scheme, $log(s_2) >= log(e)$, where $e$ is the secret to be shared. If $e$ is to be 256 bits, then $log(s_2) >= 256$ and $log(s_1) >= 768$. We have a python implementation where $log(s_1) \equiv 880$ and $log(s_2) \equiv 288$ for a total of about 1168 bits, or 146 bytes.

@@

Secondly, this feature allows for the disassociation of the distributor of the public key from the possessor of the public key. For example, assume we have three parties, Alice, Bob, and Charlie. Charlie does not want Alice to communicate with Bob. If Charlie searches Alices computer and he finds Bobs public key, then he will know that Alice has been or intended to communicate with Bob. To counter this, Alice can randomize Bobs public key and store only the randomized key. The randomized key will be functionally equivalent to the public key associated with Bob, with the exception that nobody may associate it with Bob.

Any homomorphic secret-key instantiated scheme can trivially produce a randomized public key using the secret key to generate a new public key; The scheme presented here allows for the generation of a randomized public key using only the public key. The difference is that in the former case, Bob would have to distribute the randomized key, which would associate it with him (assuming it is signed, for example). In the latter case, Bob has only one key, and Alice can obtain a randomized public key on her own.

\subsubsection{Key Randomization Algorithm}
\begin{align}
    p_n \gets p_1 r_1 - p_2 r_2 + p_1 r_3 - p_2 r_4\\
\end{align}

\section{Metrics}
Private keys are slightly less then 1200 bits or 150 bytes. Public keys are approximately 2300 bits or 280 bytes. Ciphertexts from the key exchange algorithm are about 1500 bits or 185 bytes.

The time required to generate a keypair is about .0019 seconds. Our simple python implementation can perform 8192 key exchanges in slightly less then 1 second. While a C implementation would probably be faster, most of the time is likely spent doing bignum arithmetic, which means that a simple python implementation may be acceptably fast.
